### 2013-08-29 thesis/src/chapters/chapter-2.tex
Added chapter-5 draft

It is commonly agreed that there are two main possible ways the resource can be added to a server:
\begin{itemize}
	\item \textit{horizontal scaling (scaling out)} - adding more nodes to a system, such as servers in context of distributed application
	\item \textit{vertical scaling (scaling up)} - increasing capacity of a single node in a system, i.e. adding additional memory, CPU, storage, etc.
\end{itemize}

Having that said, common sense dictates that adding resources is only a part of the success - it should be accompanied by tuning application platform configuration. For example, adding supplementary CPUs without increasing thread pools that handle request make a little sense. Similarly, we have to increase heap size, in context of a Java application, to make a good use of extra memory. While importance of application tuning cannot be underestimated, its detailed analysis lies outside of the scope of this dissertation.

@@

The rest of this chapter elaborates in details about horizontal, vertical scaling and application tuning taking into account mechanisms used in Platform-as-a-Service solutions that are available on the market.

@@

>>>>

It is commonly agreed that there are two main possible ways the resource can be added:
\begin{itemize}
	\item \textit{horizontal scaling (scaling out)} - adding more nodes to a system, such as servers in context of distributed application
	\item \textit{vertical scaling (scaling up)} - increasing capacity of a single node in a system, i.e. adding additional memory, CPU, storage, etc.
\end{itemize}

Having that said, common sense dictates that adding resources is only a part of the success - it should be accompanied by tuning application platform configuration. For example, adding supplementary CPUs without increasing thread pool size that handle requests make a little sense. Similarly, we have to increase heap size, in context of a Java application, to make a good use of extra memory. While importance of application tuning cannot be underestimated, its detailed analysis lies outside of the scope of this dissertation.

What makes scaling application particularly interesting are the benefits offered by a cloud computing, especially the illusion of a virtually infinite computing infrastructure \cite{VaRoBu11}. Making use of virtualization technologies, which often underpins cloud computing platform, allows for resource manipulation in a dynamic, on-demand manner.

@@

The rest of this chapter elaborates in details about horizontal and vertical scaling taking into account mechanisms used in Platform-as-a-Service solutions that are available on the market.

@@

As it was outlined in a previous section, vital element of horizontal scaling is adding additional resources. In context of an application execution environment, node can be represented by an application server, database or other resources that affect application performance such as network interface \cite{VaRoBu11}. Dynamic capabilities of a cloud computing platform offer a couple of ways this can be done:
\begin{itemize}
	\item virtual machine replication
	\item network slicing
	\item database replication
\end{itemize}

jebnac mapowanie na warstwy clouda - infr, platform, app

\subsection{Virtual machine replication}

\subsection{Network slicing}

\subsection{Database replication}
